Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2022-11-16 study protocol.qmd
Combined all datasets

# Table 1

atach.whole <- atach.whole %>%
  rename(age = F33Q02) %>%
  rename(symptom.onset = F00Q02MIN) %>%
  rename(sbp.initial = F05Q07A) %>%
  rename(dbp.initial = F05Q07B) %>%
  rename(gcs.baseline = F33Q04) %>%
  rename(intubation.days = F07Q02) %>%
  rename(extubation.date = F07Q03DAY) %>%
  rename(trach.date = F07Q04DAY) %>%
  rename(evd.days = F07Q07) %>%
  rename(nsgy.evacuation.date = F07Q09DAY) %>%
  rename(euro.vas.90 = F16Q07) %>%
  rename(EQ_INDEX.90 = EQ_INDEX)

VarsTableOne <- c("study",
                  "age", # Age
                       "sex", # Sex
                       "ethnicity", # Ethnicity
                       "race", # Race
                       "enrolling.country", # Country of Enrolling Site
                       "stroke", 
                       "cad", 
                       "chf", 
                       "afib", 
                       "pvd",
                       "hld",
                       "dm2",
                       "tobacco",
                       #"symptom.onset", # Time of symptom onset
                       "sbp.initial", # Initial SBP
                       "dbp.initial", # Initial DBP
                       "gcs.baseline", # Baseline GCS
                       #"nihss.baseline", # NIHSS
                       "ich.location.baseline", 
                       "ivh",
                      # "hydrocephalus",
                       "ich.volume.cc",
                       "ivh.volume.cc",
                       "phe.volume.cc",
                       "sp.shift.baseline",
                       "mech.ventilation",
                       "intubation.days", 
                       "extubation.date", # Date of extubation
                       "tracheostomy",
                       "trach.date", # Date of Tracheostomy
                       "evd",
                       "evd.days", # Total EVD days
                       "nsgy.evacuation",
                       "nsgy.evacuation.date",  # Date of Evacuation
                       "mrs.30",
                       "mrs.90",
                      "mrs.180",
                      "mrs.365",
                      "euro.mobility.90",
                      "euro.mobility.180",
                      "euro.mobility.365",
                       "euro.selfcare.90",
                      "euro.selfcare.180",
                      "euro.selfcare.365",
                       "euro.usual.90",
                      "euro.usual.180",
                      "euro.usual.365",
                       "euro.pain.90",
                      "euro.pain.180",
                      "euro.pain.365",
                       "euro.anxiety.90",
                      "euro.anxiety.180",
                      "euro.anxiety.365",
                       "euro.vas.90", # EuroQOL VAS
                       "euro.vas.180",
                       "euro.vas.365",
                       "EQ_INDEX.90", # EQ-5D Utility Index,,
                      "current.location.90",
                      "current.location.180",
                      "current.location.365",
                       "ich.laterality"
                  )

@@

erich.whole <- erich.whole %>%
  mutate(ich.location.baseline = recode(erich.case$detail,
                                        "L Thalamic" = "Thalamus",
                                        "R Thalamic" = "Thalamus",
                                        "L Caudate Nucleus" = "Basal Ganglia",
                                        "L Cerebellar" = "Cerebellum",
                                        "L Corona Radiata" = "Lobar",
                                        "L Frontal" = "Lobar",
                                        "L Frontal Temporal" = "Lobar",
                                        "L Frontoparietal" = "Lobar",
                                        "L Occipital" = "Lobar",
                                        "L Parietal" = "Lobar",
                                        "L Parieto-Occipital" = "Lobar",
                                        "L Periventricular" = "Basal Ganglia",
                                        "L Putaminal" = "Basal Ganglia",
                                        "L Temporal" = "Lobar",
                                        "L Temporal-Parietal-Occipital (L Hemisphere)" = "Lobar",
                                        "L Temporal Occipital" = "Lobar",
                                        "L Temporal parietal" = "Lobar",
                                        "Multiple Hemorrhages - Deep" = "Basal Ganglia",
                                        "Multiple Hemorrhages - Lobar" = "Lobar",
                                        "Not applicable" = "NA",
                                        "Primary IVH" = "Primary IVH",
                                        "R Basal Ganglia" = "Basal Ganglia",
                                        "R Caudate Nucleus" = "Basal Ganglia",
                                        "R Cerebellar" = "Cerebellum",
                                        "R Frontal" = "Lobar",
                                        "R Frontal Temporal" = "Lobar",
                                        "R Frontoparietal" = "Lobar",
                                        "R Occipital" = "Lobar",
                                        "R Parietal" = "Lobar",
                                        "R Parieto-Occipital" = "Lobar",
                                        "R Periventricular" = "Basal Ganglia",
                                        "R Putaminal" = "Basal Ganglia",
                                        "R Temporal" = "Lobar",
                                        "R Temporal-Parietal-Occipital (R Hemisphere)" = "Lobar",
                                        "R Temporal Occipital" = "Lobar",
                                        "R Temporal Perietal" = "Lobar",
                                        "Unknown" = "NA",
                                        "Brainstem" = "Brainstem",
                                        "Cerebellar" = "Cerebellum",
                                        "R Temporal parietal" = "Lobar",
                                        "L Basal Ganglia" = "Basal Ganglia",                                        ))

@@

@@

erich.whole$nsgy.interval <- as.period(erich.whole$symptom.onset.combined %--% erich.whole$nsgy.evacuation.date.erich)
erich.whole$nsgy.interval <- time_length(erich.whole$nsgy.interval, unit = "days")
erich.whole$nsgy.evacuation.date <- round(erich.whole$nsgy.interval, digits = 0) # Makes it compatabible to merge with ATACH

@@

@@

@@

@@

# Filtering out ICH Laterality and Infratentorial Location
erich.whole <- erich.whole %>%
  filter(ich.laterality != "NA") %>%
  filter(ich.location.baseline == "Basal Ganglia" |
           ich.location.baseline == "Thalamus" |
           ich.location.baseline == "Lobar")

@@

@@

@@

@@

clear3.whole <- clear3.whole %>%
  rename(age = age_at_registration) %>%
  rename(tobacco = tobacco_use) %>%
  rename(sbp.initial = er_present_systolic) %>%
  rename(dbp.initial = er_present_diastolic) %>%
  rename(ich.location.baseline = adjudicated_ich_location) %>%
  rename(gcs.baseline = er_present_gcs_total) %>%
  rename(nihss.baseline = er_present_nihss_total) %>%
  rename(ich.volume.cc = dct_ich_volume_rc) %>%
  rename(ivh.volume.cc = dct_ivh_volume_rc) %>%
  rename(mrs.30 = glasgow_rankin_30) %>%
  rename(mrs.180 = glasgow_rankin_180) %>%
  rename(gose.30 = gose_30) %>%
  rename(gose.180 = gose_180) %>%
  rename(comfort.binary = withdrawal_contribution) %>%
  rename(comfort.date.time = ictus_to_withdrawal_days) %>%
  rename(symptom.onset.to.presentation = ictus_to_presentation)

@@

mistie2.combined.demographics <- full_join(mistie2.demographics, mistie2.demographics3)
mistie2.combined.demographics <- full_join(mistie2.combined.demographics, mistie2.demographics2)

@@

mistie2.whole <- mistie2.whole %>%
  mutate(race = recode(Race,
                       "African American not Hispanic" = "Black or African American",
                       "Asian or Pacific Islander" = "Asian",
                       "Caucasian not Hispanic" = "White",
                       "Hispanic" = "Other/Not Reported",
                       "Other or unknown" = "Other/Not Reported"
  ))

mistie2.whole <- mistie2.whole %>%
  rename(sbp.initial = er_sbp) %>%
  rename(dbp.initial = er_dbp) %>%
  rename(gcs.baseline = enrollment_gcs) %>%
  rename(nihss.baseline = enrollment_nihss_total) %>%
  rename(ich.volume.cc = pre_rand_ichvol) %>%
  rename(ivh.volume.cc = pre_rand_ivhvol) %>%
  rename(gos.365 = GOS_365) %>%
  rename(gos.270 = GOS_270) %>%
  rename(gos.180 = GOS_180) %>%
  rename(gos.90 = GOS_90) %>%
  rename(gos.30 = GOS_30) %>%
  rename(egos.365 = eGOS_Score_365) %>%
  rename(egos.270 = eGOS_Score_270) %>%
  rename(egos.180 = eGOS_Score_180) %>%
  rename(egos.90 = eGOS_Score_90) %>%
  rename(egos.30 = eGOS_Score_30) %>%
  rename(mrs.365 = rankin_score_365) %>%
  rename(mrs.270 = rankin_score_270) %>%
  rename(mrs.180 = rankin_score_180) %>%
  rename(mrs.90 = rankin_score_90) %>%
  rename(mrs.30 = rankin_score_30)

mistie2.whole <- mistie2.whole %>%
  mutate(ivh = recode(any_ivh_prerand,
                      "0" = "No",
                      "1" = "Yes"
  ))

@@

mistie3 <- mistie3 %>%
  rename(age = age_at_consent) %>%
  rename(race = race_ninds) %>%
  rename(sbp.initial = er_present_systolic) %>%
  rename(dbp.initial = er_present_diastolic) %>%
  rename(gcs.baseline = gcs_total) %>%
  rename(nihss.baseline = nihss_total) %>%
  rename(ich.volume.cc = diagct_ich_volume) %>%
  rename(ivh.volume.cc = diagct_ivh_volume) %>%
  rename(ich.laterality = ich_hemisphere_adj) %>%
  rename(mrs.30 = glasgow_rankin_30) %>%
  rename(mrs.180 = glasgow_rankin_180) %>%
  rename(mrs.365 = glasgow_rankin_365) %>%
  rename(barthel.total.365 = barthel_index_365) %>%
  rename(eq.vas.365 = eq_vas_365) %>%
  rename(time.to.presentation = ictus_to_site_arrival_hours)

mistie3 <- mistie3 %>%
  mutate(race = case_when(
    race == "African-American" ~ "Black of African-American",
    race == "Asian Hawaiian or Pacific" ~ "Asian",
    race == "Indian or Alaskan" ~ "American Indian or Alaskan Native",
    race == "More than one race" ~ "Other/Not Reported",
    race == "White" ~ "White"
  ))

@@

mistie3 <- mistie3 %>%
  mutate(comfort = case_when(
    withdrawal_contribution == "0" ~ "No",
    withdrawal_contribution == "1" ~ "Yes"
  ))

@@

@@

```{r combining ATACH2 and ERICH}

atach.erich <- union_all(atach.whole, erich.whole)

atach.erich <- atach.erich %>%
  select(VarsTableOne) %>%
  mutate(ich.score.age = case_when(
    age < 80 ~ 0,
    age >= 80 ~ 1
  )) %>%
  mutate(ich.score.gcs = case_when(
    gcs.baseline >= 13 ~ 0,
    gcs.baseline <= 4 ~ 2,
    TRUE ~ 1)) %>%
  mutate(ich.score.volume = if_else(ich.volume.cc >= 30,1,0)) %>%
  mutate(ich.score.ivh = if_else(ivh == "Yes",1,0)) %>%
  mutate(ich.score.total = ich.score.age + 
                           ich.score.gcs + 
                           ich.score.volume +
                           ich.score.ivh)

atach.erich %>%
  as_tibble()

table1 <- CreateTableOne(data = atach.erich,
                         strata = "ich.laterality",)

print(table1, showAllLevels = FALSE)

@@

>>>>

# Renaming variables

atach.whole <- atach.whole %>%
  rename(age = F33Q02) %>%
  rename(symptom.onset = F00Q02MIN) %>% # All times in ATACH2 dataset are expressed as minutes from randomization
  rename(arrivaltime.initial = F02Q03MIN) %>% 
  rename(arrivaltime.strokecenter = F02Q05MIN) %>%
  rename(sbp.initial = F05Q07A) %>%
  rename(dbp.initial = F05Q07B) %>%
  rename(gcs.baseline = F33Q04) %>%
  rename(intubation.days = F07Q02) %>%
  rename(extubation.date = F07Q03DAY) %>%
  rename(trach.date = F07Q04DAY) %>%
  rename(evd.days = F07Q07) %>%
  rename(nsgy.evacuation.date = F07Q09DAY) %>%
  rename(euro.vas.90 = F16Q07) %>%
  rename(EQ_INDEX.90 = EQ_INDEX)

# Calculating Time to ED Presentation as expressed by minutes and hours from symptom onset

atach.whole <- atach.whole %>%
  mutate(time.to.ed.minutes = abs(arrivaltime.strokecenter - symptom.onset)) %>%
  mutate(time.to.ed.hours = time.to.ed.minutes / 60)

atach.whole$time.to.ed.hours <- round(atach.whole$time.to.ed.hours, digits = 2)

atach.times <- atach.whole %>%
  select(c(symptom.onset, arrivaltime.initial, arrivaltime.strokecenter, time.to.ed.minutes, time.to.ed.hours))

# DNR and WLST status

atach.whole <- atach.whole %>%
  mutate(dnr.binary = case_when(
    F21Q08 == "0" ~ "No",
    F21Q08 == "1" ~ "Yes"
  ))

atach.whole <- atach.whole %>%
  mutate(comfort.binary = case_when(
    F21Q06 == "0" ~ "No",
    F21Q06 == "1" ~ "Yes"
  ))

atach.whole <- atach.whole %>%
  rename(comfort.day = F21Q07DAY) %>%
  rename(dnr.day = F21Q09DAY)

@@

# ICH Location
erich.whole <- erich.whole %>%
  mutate(
    ich.location.baseline = case_when(
      str_detect(erich.whole$detail, "Ganglia") ~ "Basal Ganglia",
      str_detect(erich.whole$detail, "Brainstem") ~ "Brainstem",
      str_detect(erich.whole$detail, "Cerebell") ~ "Cerebellum",
      str_detect(erich.whole$detail, "Front") ~ "Lobar",
      str_detect(erich.whole$detail, "Tempor") ~ "Lobar",
      str_detect(erich.whole$detail, "Occi") ~ "Lobar",
      str_detect(erich.whole$detail, "Perivent") ~ "Basal Ganglia",
      str_detect(erich.whole$detail, "Caudate") ~ "Basal Ganglia",
      str_detect(erich.whole$detail, "Putam") ~ "Basal Ganglia",
      str_detect(erich.whole$detail, "Deep") ~ "Basal Ganglia",
      str_detect(erich.whole$detail, "Lobar") ~ "Lobar",
      str_detect(erich.whole$detail, "IVH") ~ "Primary IVH",
      str_detect(erich.whole$detail, "Hemis") ~ "Lobar",
      str_detect(erich.whole$detail, "Thal") ~ "Thalamus",
      str_detect(erich.whole$detail, "Ganglia") ~ "Basal Ganglia",
      str_detect(erich.whole$detail, "Corona") ~ "Lobar",
      str_detect(erich.whole$detail, "applic") ~ "NA",
      detail == "Unknown" ~ "NA"
      ))

@@

# Calculating Time to ED Presentation as expressed by minutes and hours from symptom onset

erich.whole$symptom.onset.interval <- as.period(erich.whole$symptom.onset.combined %--% erich.whole$ed.presentation.date.time)
erich.whole$time.to.ed.minutes <- time_length(erich.whole$symptom.onset.interval, unit = "minutes")
erich.whole$time.to.ed.hours <- time_length(erich.whole$symptom.onset.interval, unit = "hours")

erich.whole$time.to.ed.minutes[erich.whole$time.to.ed.minutes < 0] = NA
erich.whole$time.to.ed.hours[erich.whole$time.to.ed.hours < 0] = NA

@@

erich.whole$nsgy.interval <- as.period(erich.whole$symptom.onset.combined %--% erich.whole$nsgy.evacuation.date.erich)
erich.whole$nsgy.interval <- time_length(erich.whole$nsgy.interval, unit = "days")
erich.whole$nsgy.evacuation.date <- round(erich.whole$nsgy.interval, digits = 0) # Makes it compatible to merge with ATACH

@@

erich.whole$dnr.interval <- as.period(erich.whole$symptom.onset.combined %--% erich.whole$dnr.date.time)
erich.whole$dnr.interval <- time_length(erich.whole$dnr.interval, unit = "days")
erich.whole$dnr.day <- round(erich.whole$dnr.interval, digits = 0)

@@

erich.whole$dni.interval <- as.period(erich.whole$symptom.onset.combined %--% erich.whole$dni.date.time)
erich.whole$dni.interval <- time_length(erich.whole$dni.interval, unit = "days")
erich.whole$dni.day <- round(erich.whole$dni.interval, digits = 0)

@@

erich.whole$comfort.interval <- as.period(erich.whole$symptom.onset.combined %--% erich.whole$comfort.date.time)
erich.whole$comfort.interval <- time_length(erich.whole$comfort.interval, unit = "days")
erich.whole$comfort.day <- round(erich.whole$comfort.interval, digits = 0)

@@

@@

# Renaming Variables

clear3.whole <- clear3.whole %>%
  rename(age = age_at_registration) %>%
  rename(sbp.initial = er_present_systolic) %>%
  rename(dbp.initial = er_present_diastolic) %>%
  rename(ich.location.baseline = adjudicated_ich_location) %>%
  rename(gcs.baseline = er_present_gcs_total) %>%
  rename(nihss.baseline = er_present_nihss_total) %>%
  rename(ich.volume.cc = dct_ich_volume_rc) %>%
  rename(ivh.volume.cc = dct_ivh_volume_rc) %>%
  rename(mrs.30 = glasgow_rankin_30) %>%
  rename(mrs.180 = glasgow_rankin_180) %>%
  rename(gose.30 = gose_30) %>%
  rename(gose.180 = gose_180) %>%
  rename(comfort.day = ictus_to_withdrawal_days)

@@

clear3.whole <- clear3.whole %>%
  mutate(ich.location.baseline = case_when(
    ich.location.baseline == "Caudate" ~ "Basal Ganglia",
    ich.location.baseline == "Frontal" ~ "Lobar",
    ich.location.baseline == "Globus Pallidus" ~ "Basal Ganglia",
    ich.location.baseline == "Occipital" ~ "Lobar",
    ich.location.baseline == "Other" ~ "NA",
    ich.location.baseline == "Probable Primary IVH" ~ "Primary IVH",
    ich.location.baseline == "Putamen" ~ "Basal Ganglia",
    ich.location.baseline == "Temporal" ~ "Lobar",
    ich.location.baseline == "Thalamus" ~ "Thalamus"
  ))

@@

clear3.whole <- clear3.whole %>%
  mutate(tobacco = recode(tobacco_use,
                          "1" = "Yes",
                          "NA" = "No"))

@@

clear3.whole <- clear3.whole %>%
  mutate(comfort.binary = case_when(
    withdrawal_contribution == "on" ~ "Yes",
    TRUE ~ "No"
  ))

# Recalculating Time to ED Presentation

clear3.whole <- clear3.whole %>%
  mutate(time.to.ed.minutes = ictus_to_presentation*24*60) %>%
  mutate(time.to.ed.hours = ictus_to_presentation*24)

clear3.whole$time.to.ed.minutes <- round(clear3.whole$time.to.ed.minutes, digits = 0)
clear3.whole$time.to.ed.hours <- round(clear3.whole$time.to.ed.hours, digits = 2)

@@

mistie2.combined.demographics <- left_join(mistie2.demographics3, mistie2.demographics)
mistie2.combined.demographics <- left_join(mistie2.demographics2, mistie2.combined.demographics)

@@

mistie2.whole <- mistie2.whole %>%
  mutate(race = recode(Race,
                       "African American not Hispanic" = "Black or African-American",
                       "Asian or Pacific Islander" = "Asian",
                       "Caucasian not Hispanic" = "White",
                       "Hispanic" = "Other/Not Reported",
                       "Other or unknown" = "Other/Not Reported"
  ))

mistie2.whole <- mistie2.whole %>%
  mutate(ich.location.baseline = case_when(
    clot_location_rc == "Globus Palidus" ~ "Basal Ganglia",
    clot_location_rc == "Lobar" ~ "Lobar",
    clot_location_rc == "Putamen" ~ "Basal Ganglia",
    clot_location_rc == "Thalamus" ~ "Thalamus"
  ))

mistie2.whole <- mistie2.whole %>%
  mutate(ivh = recode(any_ivh_prerand,
                      "1" = "Yes",
                      "0" = "No",
                      .default = "NA"
  ))

mistie2.whole <- mistie2.whole %>%
  rename(sbp.initial = er_sbp) %>%
  rename(dbp.initial = er_dbp) %>%
  rename(gcs.baseline = enrollment_gcs) %>%
  rename(nihss.baseline = enrollment_nihss_total) %>%
  rename(ich.volume.cc = pre_rand_ichvol) %>%
  rename(ivh.volume.cc = pre_rand_ivhvol) %>%
  rename(htn = Hypertension) %>%
  rename(hld = Hyperlipidemia) %>%
  rename(dm2 = Diabetes) %>%
  rename(tobacco = Tobacco_Use) %>%
  rename(cad = Other_CV) %>%
  rename(gos.365 = GOS_365) %>%
  rename(gos.270 = GOS_270) %>%
  rename(gos.180 = GOS_180) %>%
  rename(gos.90 = GOS_90) %>%
  rename(gos.30 = GOS_30) %>%
  rename(egos.365 = eGOS_Score_365) %>%
  rename(egos.270 = eGOS_Score_270) %>%
  rename(egos.180 = eGOS_Score_180) %>%
  rename(egos.90 = eGOS_Score_90) %>%
  rename(egos.30 = eGOS_Score_30) %>%
  rename(mrs.365 = rankin_score_365) %>%
  rename(mrs.270 = rankin_score_270) %>%
  rename(mrs.180 = rankin_score_180) %>%
  rename(mrs.90 = rankin_score_90) %>%
  rename(mrs.30 = rankin_score_30) %>%
  rename(ich.laterality = hemisphere)

@@

mistie3 <- mistie3 %>%
  rename(age = age_at_consent) %>%
  rename(race = race_ninds) %>%
  rename(sbp.initial = er_present_systolic) %>%
  rename(dbp.initial = er_present_diastolic) %>%
  rename(gcs.baseline = gcs_total) %>%
  rename(nihss.baseline = nihss_total) %>%
  rename(ich.volume.cc = diagct_ich_volume) %>%
  rename(ivh.volume.cc = diagct_ivh_volume) %>%
  rename(ich.laterality = ich_hemisphere_adj) %>%
  rename(mrs.30 = glasgow_rankin_30) %>%
  rename(mrs.180 = glasgow_rankin_180) %>%
  rename(mrs.365 = glasgow_rankin_365) %>%
  rename(barthel.total.365 = barthel_index_365) %>%
  rename(eq.vas.365 = eq_vas_365) %>%
  rename(time.to.ed.hours = ictus_to_diagct_hours)

mistie3$time.to.ed.hours = round(mistie3$time.to.ed.hours, digits = 2)
mistie3$time.to.ed.minutes = mistie3$time.to.ed.hours * 60
mistie3$time.to.ed.minutes = round(mistie3$time.to.ed.minutes, digits = 0)

mistie3 <- mistie3 %>%
  mutate(race = case_when(
    race == "African-American" ~ "Black or African-American",
    race == "Asian Hawaiian or Pacific" ~ "Asian",
    race == "Indian or Alaskan" ~ "American Indian or Alaskan Native",
    race == "More than one race" ~ "Other/Not Reported",
    race == "White" ~ "White"
  ))

@@

mistie3 <- mistie3 %>%
  mutate(ich.location.baseline = case_when(
    ich_location_specify == "BG" ~ "Basal Ganglia",
    ich_location_specify == "Frontal" ~ "Lobar",
    ich_location_specify == "Occipital" ~ "Lobar",
    ich_location_specify == "Parietal" ~ "Lobar",
    ich_location_specify == "Temporal" ~ "Lobar",
    ich_location_specify == "Thalamus" ~ "Thalamus",
  ))

mistie3 <- mistie3 %>%
  mutate(comfort.binary = case_when(
    withdrawal_contribution == "0" ~ "No",
    withdrawal_contribution == "1" ~ "Yes"
  ))

mistie3 <- subset(mistie3, select = -withdrawal_contribution)

@@

# Calculating WLST Day

mistie3 <- mistie3 %>%
  mutate(symptom.onset.date = mdy(ninds_symptom_onset_date)) %>%
  mutate(withdrawal.date = mdy(ninds_withdrawal_date))

mistie3$withdrawal.interval <- as.period(mistie3$symptom.onset.date %--% mistie3$withdrawal.date)
mistie3$withdrawal.interval <- time_length(mistie3$withdrawal.interval, unit = "days")
mistie3$comfort.day <- round(mistie3$withdrawal.interval, digits = 0)

@@

```{r Combining Everything}

# Combining Data from All Studies
combined.dataset.list <- list(atach.whole, erich.whole, clear3.whole, mistie2.whole, mistie3)

atach.erich <- full_join(atach.whole, erich.whole)
atach.erich.clear <- full_join(atach.erich, clear3.whole)
atach.erich.clear.mistie2 <- full_join(atach.erich.clear, mistie2.whole)
atach.erich.clear.mistie2.mistie3 <- full_join(atach.erich.clear.mistie2, mistie3)

VarsTableOne <- c("study","age", "sex", "ethnicity", # Ethnicity
                       "race", # Race
                       "enrolling.country", # Country of Enrolling Site
                       "stroke", 
                       "cad", 
                       "chf", 
                       "afib", 
                       "pvd",
                       "hld",
                       "dm2",
                       "tobacco",
                       "time.to.ed.minutes", # Time from symptom onset to Ed presentation
                       "sbp.initial", # Initial SBP
                       "dbp.initial", # Initial DBP
                       "gcs.baseline", # Baseline GCS
                       "nihss.baseline", # NIHSS
                       "ich.location.baseline", 
                       "ivh",
                      # "hydrocephalus",
                       "ich.volume.cc",
                       "ivh.volume.cc",
                       "phe.volume.cc",
                       "sp.shift.baseline",
                       "mech.ventilation",
                       "intubation.days", 
                       "extubation.date", # Date of extubation
                       "tracheostomy",
                       "trach.date", # Date of Tracheostomy
                       "evd",
                       "evd.days", # Total EVD days
                       "nsgy.evacuation",
                       "nsgy.evacuation.date",  # Date of Evacuation
                       "mrs.30",
                       "mrs.90",
                      "mrs.180",
                      "mrs.365",
                      "euro.mobility.90",
                      "euro.mobility.180",
                      "euro.mobility.365",
                       "euro.selfcare.90",
                      "euro.selfcare.180",
                      "euro.selfcare.365",
                       "euro.usual.90",
                      "euro.usual.180",
                      "euro.usual.365",
                       "euro.pain.90",
                      "euro.pain.180",
                      "euro.pain.365",
                       "euro.anxiety.90",
                      "euro.anxiety.180",
                      "euro.anxiety.365",
                       "euro.vas.90", # EuroQOL VAS
                       "euro.vas.180",
                       "euro.vas.365",
                       "EQ_INDEX.90", # EQ-5D Utility Index,,
                      "current.location.90",
                      "current.location.180",
                      "current.location.365",
                       "ich.laterality",
                  "dnr.binary",
                  "comfort.binary",
                  "dnr.day",
                  "comfort.day"
                  )

ninds.combined <- atach.erich.clear.mistie2.mistie3 %>%
  select(VarsTableOne)

ninds.combined <- ninds.combined %>%
  mutate(ich.score.age = case_when(
    age < 80 ~ 0,
    age >= 80 ~ 1
  )) %>%
  mutate(ich.score.gcs = case_when(
    gcs.baseline >= 13 ~ 0,
    gcs.baseline <= 4 ~ 2,
    TRUE ~ 1)) %>%
  mutate(ich.score.volume = if_else(ich.volume.cc >= 30,1,0)) %>%
  mutate(ich.score.ivh = if_else(ivh == "Yes",1,0)) %>%
  mutate(ich.score.total = ich.score.age + 
                           ich.score.gcs + 
                           ich.score.volume +
                           ich.score.ivh)

# Cleaning up combined dataset
ninds.combined <- ninds.combined %>%
  mutate(sex = case_when(
    sex == "Man" ~ "Male",
    sex == "Male" ~ "Male",
    sex == "Woman" ~ "Female",
    sex == "Female" ~ "Female")) %>%
  mutate(ethnicity = case_when(
    ethnicity == "Hispanic or Latino" ~ "Hispanic or Latino",
    ethnicity == "Not Hispanic or Latino" ~ "Not Hispanic or Latino",
    ethnicity == "Unknown/Not Reported" ~ "NA")) %>%
  mutate(ich.location.baseline = case_when(
    ich.location.baseline == "Basal Ganglia" ~ "Basal Ganglia",
    ich.location.baseline == "Brainstem" ~ "Brainstem",
    ich.location.baseline == "Caudate" ~ "Basal Ganglia",
    ich.location.baseline == "Cerebellum" ~ "Cerebellum",
    ich.location.baseline == "Frontal" ~ "Lobar",
    ich.location.baseline == "Globus Pallidus" ~ "Basal Ganglia",
    ich.location.baseline == "Lobar" ~ "Lobar",
    ich.location.baseline == "Occipital" ~ "Lobar",
    ich.location.baseline == "Other" ~ "Other",
    ich.location.baseline == "Parietal" ~ "Lobar",
    ich.location.baseline == "Primary IVH" ~ "Primary IVH",
    ich.location.baseline == "Probable Primary IVH" ~ "Primary IVH",
    ich.location.baseline == "Putamen" ~ "Basal Ganglia",
    ich.location.baseline == "Temporal" ~ "Lobar",
    ich.location.baseline == "Thalamus" ~ "Thalamus"
  ))

ninds.combined <- ninds.combined %>%
  filter(ich.location.baseline == "Lobar" | 
           ich.location.baseline == "Thalamus" |
           ich.location.baseline == "Basal Ganglia") %>%
  filter(!is.na(ich.laterality))

table1 <- CreateTableOne(data = ninds.combined,
                         strata = "ich.laterality")

@@

```{r output = TRUE}
print(table1, showAllLevels = FALSE)
